The error in Bayesian phylogenetic reconstruction when speciation co-occurs

### 2020-01-23 razzo-hypotheses.tex

$\mathcal{H}_4$: RJCB expects that, on average, the inference error is equal for
parameter settings with an equal $\lambda$, $\nu$ and $q$, i.e. extinction
has no effect on the error made, because extinction affects all species equally. 
\richel{figure 1a and b, or a new figure}
\giovanni{A higher extinction rate increases variance and tend to reduce to number of taxa in the tree. According to your other hypotheses (e.g. H5) these effects do affect the inference. Therefore you need to adjust for these variables to prove your hypothesis.}

@@

$\mathcal{H}_9$: GL expects a positive correlation between $\nu \, q(1-q)$ and the error made by the inference process. This is due to the fact that this factor regulates the variance of the underlying binomial distribution that regulates multiple births events.

>>>>

$\mathcal{H}_4$: RJCB expects that, on average, the inference error is equal for
parameter settings with an equal $\lambda$, $\nu$ and $q$, i.e. extinction
has no effect on the error made, because extinction affects all species equally. 
\richel{figure 1a and b, or a new figure}
\giovanni{A higher extinction rate increases variance and tends to reduce to number of taxa in the tree. According to your other hypotheses (e.g. H5) these effects do affect the inference. Therefore you need to adjust for these variables to prove your hypothesis.}

@@

$\mathcal{H}_9$: GL expects a positive correlation between $\nu \, q(1-q)$ and the error made by the inference process. This is due to the fact that this factor expresses the variance of the underlying binomial distribution that regulates multiple births events.
